Conservation of interaction partners between related plants varies widely across communities and between plant families.

### 2019-07-31 manuscript/phylogenetic_signal_manuscript.tex
found Christie still in author contributions

  If attractive and/or defensive traits are heritable,
  then we can reasonably expect that related plants will have similar 
  patterns of interactions with animals, especially if there is some selection in either group to avoid competition or the number of potential partners is limited~\citep{Schemske1999,Ponisio2017}. That is, there may be \emph{phylogenetic signal} in plants' interactions such that closely-related plants may tend to have similar interaction partners.
  Recent studies that have investigated this question at the level of whole
  communities, however, have yielded mixed results~\citep{Rezende2007a,Gomez2010,Rohr2014a,Fontaine2015,Lind2015,Ibanez2016,Bergamini2017,Sydenham2017,Volf2017,Hutchinson2017}.
  In particular, significant phylogenetic signal in plants' sets of interaction partners tends to be rare in empirical networks (\citealp{Rezende2007a,Lind2015,Ibanez2016}; but see~\citealp{Elias2013,Fontaine2015,Hutchinson2017}). 
  Moreover, statistically significant degrees of phylogenetic signal or coevolution may only result in small differences in network structure, adding to the difficulty of understanding patterns in species' interaction partners~\citep{Ponisio2017}.
  Further, the plant and animal components of networks can show different degrees of phylogenetic conservation of interaction partners. In mutualistic networks, animals often show a stronger phylogenetic signal in their partners than do plants~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015,Fontaine2015} (but see~\citet{Rafferty2013} for a counterexample). In antagonistic networks, however, actively-foraging consumers tend to show less phylogenetic signal than their prey~\citep{Ives2006,Cagnolo2011,Naisbit2011,Fontaine2015}. Thus, it is not straightforward to assume that interactions will always be similar among related species. [[GVDR was skeptical of a similar point in the previous draft - less contentious now?]]
  % Further, plants' roles [[how defined?]] within networks tend to be less phylogenetically constrained than those of 
  % animals~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015}. [[GVDR is skeptical of this - check partiteness, size, type of role and add more detail to support.]] % I doubt this is really important, probably more trouble than it's worth.

@@

  The variability of the strength of phylogenetic signal across networks 
  and the lack of influence of community composition on the strength of 
  the relationship between phylogenetic distance and interaction partner
  overlap could be partly due to the different trends within families. 
  More than half of the plant families in each network type
  behaved as we hypothesised, with more 
  closely-related plants having greater niche overlap than 
  distantly related plants. This relationship between overlap and 
  phylogenetic distance is consistent with the idea that traits affecting 
  interactions are heritable and change gradually
  such that closely related plants resemble their common ancestor--- and
  each other ---more than they do distantly related 
  plants~\citep{Schemske1999,Gilbert2015,Ponisio2017}. The degree of 
  heritability of key traits may, however, differ between families. In
  some families, such as \emph{Asteraceae} in pollination networks, 
  the positive slope of this relationship was very shallow while in 
  others, such as \emph{Melastomataceae} in herbivory networks, the 
  positive slope was extremely steep. This could indicate different 
  rates of phenotypic drift or evolution in different families. 
  In other families, there was no significant relationship between phylogenetic
  distance and interaction partner overlap. In these cases, key traits affecting 
  plant-insect interactions may not be strongly
  conserved. Studies showing a stronger relationship between trait similarity
  and shared interaction partners than phylogenetic similarity and shared
  interaction partners suggest that traits may indeed be evolutionarily
  labile~\citep{Junker2015,Ibanez2016,Endara2017}. 
  [[Josh had some objections to this paragraph, but I didn't quite understand what he was going for. Clearer now?]]

@@

  We thank Christiee J. Webber [[and others?]] for comments on the design of the 
  study and for data collection. 
  We also thank the authors of the published networks used in this study. 
  We are grateful for the use of the Edward Percival field station in Kaikoura, 
  New Zealand in May, 2014. This research was supported by an NSERC PGS-D 
  graduate scholarship (to ARC), a Marsden Fund Fast-Start grant (UOC-1101) and a 
  Rutherford Discovery Fellowship, both administered by the Royal Society of New 
  Zealand (to DBS), a BlueFern HPC PhD scholarship (to NJB), and by
  the Allan Wilson Centre (to GVDR).

@@

  ARC, DBS, GVDR, and NJB designed the research. ARC, MO, IN, and IMW, JAT, and CJW collected published data. 
  ARC and GVDR performed the analyses. All authors contributed to the manuscript.

>>>>

  If attractive and/or defensive traits are heritable,
  then we can reasonably expect that related plants will have similar 
  patterns of interactions with animals, especially if there is some selection in either group to avoid competition or the number of potential partners is limited~\citep{Schemske1999,Ponisio2017}. That is, there may be \emph{phylogenetic signal} in plants' interactions such that closely-related plants may tend to have similar interaction partners.
  Recent studies that have investigated this question at the level of whole
  communities, however, have yielded mixed results~\citep{Rezende2007a,Gomez2010,Rohr2014a,Fontaine2015,Lind2015,Ibanez2016,Bergamini2017,Sydenham2017,Volf2017,Hutchinson2017}.
  In particular, significant phylogenetic signal in plants' sets of interaction partners tends to be rare in empirical networks (\citealp{Rezende2007a,Lind2015,Ibanez2016}; but see~\citealp{Elias2013,Fontaine2015,Hutchinson2017}). 
  Moreover, statistically significant degrees of phylogenetic signal or coevolution may only result in small differences in network structure, adding to the difficulty of understanding patterns in species' interaction partners~\citep{Ponisio2017}.
  Further, the plant and animal components of networks can show different degrees of phylogenetic conservation of interaction partners. In mutualistic networks, animals often show a stronger phylogenetic signal in their partners than do plants~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015,Fontaine2015} (but see~\citet{Rafferty2013} for a counterexample). In antagonistic networks, however, actively-foraging consumers tend to show less phylogenetic signal than their prey~\citep{Ives2006,Cagnolo2011,Naisbit2011,Fontaine2015}. Thus, it is not straightforward to assume that interactions will always be similar among related species.

@@

  The variability of the strength of phylogenetic signal across networks 
  and the lack of influence of community composition on the strength of 
  the relationship between phylogenetic distance and interaction partner
  overlap could be partly due to the different trends within families. 
  More than half of the plant families in each network type
  behaved as we hypothesised, with more 
  closely-related plants having greater niche overlap than 
  distantly related plants. This relationship between overlap and 
  phylogenetic distance is consistent with the idea that traits affecting 
  interactions are heritable and change gradually
  such that closely related plants resemble their common ancestor--- and
  each other ---more than they do distantly related 
  plants~\citep{Schemske1999,Gilbert2015,Ponisio2017}. The degree of 
  heritability of key traits may, however, differ between families. In
  some families, such as \emph{Asteraceae} in pollination networks, 
  the positive slope of this relationship was very shallow while in 
  others, such as \emph{Melastomataceae} in herbivory networks, the 
  positive slope was extremely steep. This could indicate different 
  rates of phenotypic drift or evolution in different families. 
  In other families, there was no significant relationship between phylogenetic
  distance and interaction partner overlap. In these cases, key traits affecting 
  plant-insect interactions may not be strongly
  conserved. Studies showing a stronger relationship between trait similarity
  and shared interaction partners than phylogenetic similarity and shared
  interaction partners suggest that traits may indeed be evolutionarily
  labile~\citep{Junker2015,Ibanez2016,Endara2017}.

@@

  We thank Christiee J. Webber for comments on the design of the 
  study and for data collection. 
  We also thank the authors of the published networks used in this study. 
  We are grateful for the use of the Edward Percival field station in Kaikoura, 
  New Zealand in May, 2014. This research was supported by an NSERC PGS-D 
  graduate scholarship (to ARC), a Marsden Fund Fast-Start grant (UOC-1101) and a 
  Rutherford Discovery Fellowship, both administered by the Royal Society of New 
  Zealand (to DBS), a BlueFern HPC PhD scholarship (to NJB), and by
  the Allan Wilson Centre (to GVDR).

@@

  ARC, DBS, GVDR, and NJB designed the research. ARC, MO, IN, IMW, and JAT collected published data. 
  ARC and GVDR performed the analyses. All authors contributed to the manuscript.
